BIOL 274 Homework 2

### 2024-01-27 bio_dynamics/bio274_hw2.Rmd
q3 hw2

---
title: "BIOL 274 Homework 2"
author: "Ruby Krasnow"
date: "2024-01-26"
output: pdf_document
---

@@

## Question 2
Using Bernoulli's method, find a solution to the IVP representing the situation in #1b.

@@

>>>>

---
title: "BIOL 274 Homework 2"
author: "Ruby Krasnow"
date: "2024-01-27"
output: pdf_document
---

@@

## Question 2 - for practice
Using Bernoulli's method, find a solution to the IVP representing the situation in #1b.

@@

## Question 3
Figure 1.3.1 below is from your textbook. It shows an example of the logistic growth curve
when $p(0) << N_0/a$. How would this curve change if $N_0 < aP(0)$?

$$P(t)=\frac{N_0P_0}{aP_0+\left(N_0-aP_0\right)e^{-N_0t}}$$

```{r}
N0 = 0.1
a=0.003
p0_small=10
p0_big=50

x<-c(1:100)

ggplot()+
  geom_hline( linetype="dashed", aes(color="N0/a",yintercept=N0/a))+
  geom_line(aes(x=x, y=(N0*p0_small)/(a*p0_small+(N0-a*p0_small)*exp(-N0*x)), color="p0 << N0/a"))+
  geom_line(aes(x=x, y=(N0*p0_big)/(a*p0_big+(N0-a*p0_big)*exp(-N0*x)), color="p0 > N0/a"))+
  theme_bw()+
  labs(x="t", y="P", color=NULL)+
  scale_color_manual(values=c("gray", "#0f85a0", "#dd4124"))+
  ylim(0, NA)
```

If $N_0 < aP(0)$, that means that $N_0/a < P(0)$, or equivalently, $P(0)>N_0/a$. This is saying that our initial population size $P(0)=P_0$ is greater than our carrying capacity $N_0/a$, so the population size will decrease until it reaches the asymptote at $K=N_0/a$.

## Question 4 & 5
For problems 4 and 5, use Euler’s Method with the given step size, h, to approximate the solution
to the given IVP over the time interval specified. Your answer should include a table of
approximate values of the dependent variable. It should also include a sketch of the graph
of the approximate solution.
